---
title: "Nexus Query Terms"
author: "Alex Stephenson"
date: "29/10/2020"
output:
  html_document: default
  word_document: default
---

*Guide for use*: The below is all the potential search terms to use with nexus. Start by searching (using the search function) for the name of the company you want + query, e.g. 'AGL Energy Query'. Then copy everything in that section, and paste into Nexus. 


### AGL Energy query:

```{r message=F, echo=F, warning=F}
library(tidyverse)
library(readxl)


data <- read_xlsx('ALex.xlsx')


names<- c('search_1', 'term', 'search_2')

colnames(data) <- names



text <- paste(unlist(data$search_2), collapse =" OR ")

data$search_2 <- text

data_2 <- head(data, n = 21)

engagement_terms <- paste(unlist(na.omit(data$term)), collapse =" OR ")

data_2$term <- engagement_terms

data_2$search_1 <- paste0(data_2$search_1, ' AND')
data_2$search_2 <- paste0('AND ', data_2$search_2)




data_2$all_terms <- paste(data_2$search_1, data_2$term, data_2$search_2, sep = ' ')
                            

print(data_2$all_terms[1])


#writexl::write_xlsx(data_2,'alex_separate_cols.xlsx')

```


### AES Query

```{r}
print(data_2$all_terms[2])

```


### AGL Query

```{r}
print(data_2$all_terms[3])

```



### CEZ Query


```{r}
print(data_2$all_terms[4])

```


### Dominion Energy Query
```{r}
print(data_2$all_terms[5])

```


### Duke Query

```{r}
print(data_2$all_terms[6])

```

### Duke Energy Query
```{r}
print(data_2$all_terms[7])

```


### Е.ON Query
```{r}
print(data_2$all_terms[8])

```



### EON Query
```{r}
print(data_2$all_terms[9])

```


### Iberdrola Query
```{r}
print(data_2$all_terms[10])

```


### KEPCO Query
```{r}
print(data_2$all_terms[11])

```



### Korea Electric Power Corp Query

```{r}
print(data_2$all_terms[12])

```


### Nextera Energy Query
```{r}
print(data_2$all_terms[13])

```



### NTPC Query
```{r}
print(data_2$all_terms[14])

```


### Origin Query

```{r}
print(data_2$all_terms[15])

```

### Origin Energy Query
```{r}
print(data_2$all_terms[16])

```


### PGE Query
```{r}
print(data_2$all_terms[17])

```


### RWE Query
```{r}
print(data_2$all_terms[18])

```


### Southern Company Query
```{r}
print(data_2$all_terms[19])

```



### Tokyo Electric Power Query
```{r}
print(data_2$all_terms[20])

```


### TEPCO Query

```{r}
print(data_2$all_terms[21])

```


```{r message=F, echo =F, warning=F}
#data_3 <- as.data.frame(paste(data_2$search_1, data_2$term, data_2$search_2))


#write_csv(data_3, 'alex_one_col.csv')

```


